Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-02 sections/related.tex
Update on Overleaf.

Many libraries support BLAS plus a few sparse array types, typically CSR, CSC, BCSR, Banded, and COO.
%
Examples include Scipy, PETSc, Armadillo, OSKI, Cyclops, MKL (add cite), and Eigen~\cite{virtanen2020scipy, abhyankarpetsc, Rumengan2021, vuduc2005oski,solomonik2013cyclops, eigenweb}.
%
There are even libraries for very specific kernels and format combinations, such as SPLATT~\cite{smith2015splatt}.
%
Several of these libraries also feature some graph or mesh algorithms built on sparse matrices.
%
GraphBlas exemplifies this pattern with support for many sparse matrix operations on a variety of formats~\cite{kepner2016mathematical} although a variety of other graph libraries adopt a similar approach such as LAgraph or GBase~\cite{mattson2019lagraph, kang2011gbase} among many others~\cite{ashari2014fast,huang2020ge}.
%
In ML, several frameworks offer this type of support, most notably TorchSparse, which supports a few arrays an few operations on them~\cite{tang2022torchsparse, tang2023torchsparse++}.
%

>>>>

Many libraries support BLAS plus a few sparse array types, typically CSR, CSC, BCSR, Banded, and COO.
%
Examples include Scipy, PETSc, Armadillo, OSKI, Cyclops, MKL (add cite), and Eigen~\cite{virtanen2020scipy, abhyankarpetsc, Rumengan2021, vuduc2005oski,solomonik2013cyclops, eigenweb}.
%
There are even libraries for very specific kernels and format combinations, such as SPLATT~\cite{smith2015splatt}.
%
Several of these libraries also feature some graph or mesh algorithms built on sparse matrices.
%
GraphBlas exemplifies this pattern with support for many sparse matrix operations on a variety of formats~\cite{kepner2016mathematical} although a variety of other graph libraries adopt a similar approach such as LAgraph or GBase~\cite{mattson2019lagraph, kang2011gbase} among many others~\cite{ashari2014fast,huang2020ge}.
%
In ML, several frameworks offer this type of support, most notably TorchSparse, which supports a few arrays and a few operations on them~\cite{tang2022torchsparse, tang2023torchsparse++}.
%
